\documentclass[]{article}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{url}

\usepackage{times}

\newcommand{\comment}[1]{}

\title{CS252:BOX FILLING GAME}
\author{
\begin{tabular}{cc}
	Danaram Meghwal(11231) & Sahil Solanki(11624) \\
	\url{danaram@iitk.ac.in} & \url{ssolanki@iitk.ac.in} \\
	\multicolumn{2}{c}{Indian Institute of Technology, Kanpur}
\end{tabular}
}
\date{Final report \\	% replace by ``initial'' or ``final'' as appropriate
15th April, 2013}	% replace by actual date of submission or \today

\begin{document}

\maketitle

\begin{abstract}
	%
	Box filling game
	%
\end{abstract}


\section{Problem Statement}
In this game there are dots at rectangular positions and 
each person draws a line between 2 points either horizontally
or vertically, if it makes a square/rectangle (i.e. joining 4 nearby dots) 
then same person get the chance to draw another line.
The person who made most number of squares/rectangles wins the game.

\section{Method Used and Explanation}
  Here Python is used as programming language.Muliple
player can play this game by puting line between two points
one by one.So finally person who have most numer of squares won the match.
It takes number of dots player want and number of players from terminal. maximum 4 player can play at a time.\\
  I define a class for every player with two function one initializing player and seconf for update it.
Tkinter is used for frame and messegebox.I divided the frame in two parts one for result and other for as game dots.
when user click between two dots a line appear and turn goes to 2nd player and so on.Everytime when
a new box made it check for game is finished or not and finally shows result of game when gameover.

\section{Results}
Results of game is shown by a messege box\\
For some input outfut is as follow:\\
\begin{table}[ht]
\caption{Nonlinear Model Results}
% title of Table
\centering
% used for centering table
\begin{tabular}{c c c c}
% centered columns (4 columns)
\hline\hline
%inserts double horizontal lines
Serial no. & Case & output\\ [0.1ex]
% inserts table
%heading
\hline
% inserts single horizontal line
1 & player\ \textgreater 5 or \textless 2  & Takes input again\\
% inserting body of the table
2 & Normal Termination & winner name and full score \\
3 & Equal square & All players having draw \\ [1ex]
% [1ex] adds vertical space
\hline
%inserts single line
\end{tabular}
\label{table:nonlin}
% is used to refer this table in the text
\end{table}

\section{Conclusions and Improvements}

So we can play this game just compiling source code of python file and Enjoy the game with friends.\\
This game further be improved by taking input for game screen not from terminal and can be modified as 
a webgame using pyjs or other tools.

\end{document}
